Virtualization of a Real-Time Operating System for Robot Control with a Focus on Real-Time Compliance

### 2024-09-02 Paper.tex
rtos

\begin{multicols}{2}
  \abstract{This thesis investigates the virtualization of a Real-Time Operating System, which is built with Yocto, employs hard real-time through Xenomai 3, and is emulated using QEMU/KVM. The primary objective was to bridge the latency gap between virtualized and bare metal versions to ensure deterministic and reliable behavior, which is decisive for real-time robotics. Initial latency measurements showed a high gap between bare metal and virtualized setups. Extensive tunings across BIOS, kernel, host OS, QEMU/KVM, and guest OS were performed, which reduced the worst-case latency from 707.622~µs to 17.134~µs, close to the bare metal performance of 10.709~µs. The improvement was validated using a robotic application, comparing the tuned virtualization with the untuned and bare metal versions.} {Virtualization, Real-Time Systems, Latency Reduction, Robot Control}

>>>>

\begin{multicols}{2}
  \abstract{This thesis investigates the virtualization of a real-time operating system, which is built with Yocto, employs hard real-time through Xenomai 3, and is emulated using QEMU/KVM. The primary objective was to bridge the latency gap between virtualized and bare metal versions to ensure deterministic and reliable behavior, which is decisive for real-time robotics. Initial latency measurements showed a high gap between bare metal and virtualized setups. Extensive tunings across BIOS, kernel, host OS, QEMU/KVM, and guest OS were performed, which reduced the worst-case latency from 707.622~µs to 17.134~µs, close to the bare metal performance of 10.709~µs. The improvement was validated using a robotic application, comparing the tuned virtualization with the untuned and bare metal versions.} {Virtualization, Real-Time Systems, Latency Reduction, Robot Control}
